|

### 2025-06-19 posts/ethics/KenkyuRinri2025_slides.qmd
dropped xaringanExtra library

---
title: |
  | 研究倫理
subtitle: |
  | 2025年6月19日(木)
  | 開発研究センター
  | ミクロ経済分析研究グループ
author: "伊藤成朗"
engine: knitr
format:
  revealjs: 
    standalone: true
    embed-resources: true
    slide-number: true
    width: 1600
    height: 900
    preview-links: auto
    logo: images/quarto.png
    footer: <http://seiroito.github.io/QuartoFiles/Horton/Horton2025_slides.html>
    theme: sky
lightbox: auto
include-in-header:
  - text: |
      <style>
      #title-slide
       .title {
        font-size: 2.0em;
      }
      </style>
bibliography: ../seiro.bib
#### If it is 2 levels up, ../../seiro.bib
resources:
  - KenkyuRinri2025_slides.pdf
#### quarto render KenkyuRinri2025_slides.qmd
---
```{r read RefManageR library, echo=FALSE, warning = F}
library(RefManageR)
```
```{r setting, eval = T, cache = T, warning = F, message = F, echo = F}
library(RefManageR)
myBib <- ReadBib("c:/seiro/settings/TeX/seiro.bib")
BibOptions(max.names = 3)
```
```{r flair_color, eval = F, echo=FALSE}
library(flair)
red <- "#FF0000"
green <- "#00FF00"
blue <- "#0000FF"
```
```{css echo=FALSE}
.red {color: #FF0000;}
Green {color: #00FF00;}
.blue {color: #0000FF;}
White {
  color: white;
}
LightBlue {
  color: #33E7FF;
}
DarkBlue {
  color: #010638;
}
DBlue {
  color: dodgerblue;
}
Red {
  color: red;
}
Orange {
  color: #ff8442;
}
Yellow {
  color: yellow;
}
#### @font-face {
####   font-family: "hiragino";
####   #### src: url(../../../../../settings/fonts/HiraginoMinchoProW3.otf");
####   src: url("c:/seiro/settings/fonts/HiraginoMinchoProW3.otf");
#### }
@font-face {
  font-family: "Roboto";
  src: url("c:/seiro/settings/fonts/Roboto-Regular.ttf");
}
#### h1 {
####   font-size: 42pt;
####   font-family: 'hiragino';
####   color: black;
####   border-bottom: 1px;
####   border-color: rgb(248, 250, 252);
####   padding-bottom: 0pt;
#### }
p {
  #### font-size: 32pt;
  font-family: 'Roboto';
  color:white
}
.title{
  background-color=#010638;
}

@@

See a list of QRPs used in Dutch national survey (DNSRI) summarised [here](https://htmlpreview.github.io/?https://github.com/SeiroIto/PaperNotes/blob/main/QRPsInDutchNationalSurvey_Tufte.html)

@@

:::: {.fragment}
::: {style="font-size:80%"}
* [Allegation](https://datacolada.org/109): Data tampering in several of her work on dishonesty (incl. with Dan Ariely!)  
* HBS: Put Gino on an unpaid admin leave, hired file forensic investigators, sent retraction requests to journals  
* Gino: Sued these folks and Harvard, asking for "at least $25 million" ([para 24, main document](https://www.courtlistener.com/docket/67659904/1/gino-v-president-and-fellows-of-harvard-college/))  
* [The problem, though, is that it will take years --- and be extraordinarily expensive --- to settle](https://www.vox.com/future-perfect/2023/8/9/23825966/francesca-gino-honesty-research-scientific-fraud-defamation-harvard-university#:~:text=The%20problem%2C%20though%2C%20is%20that%20it%20will%20take%20years%20%E2%80%94%20and%20be%20extraordinarily%20expensive%20%E2%80%94%20to%20settle)
* [150人あまりの共著者たちはどの論文は不正がないか調べる羽目に](https://www.science.org/content/article/after-honesty-researcher-s-retractions-colleagues-expand-scrutiny-her-work#:~:text=This%20week%2C%20Simonsohn%20and%20five%20other%20Gino%20co%2Dauthors%20emailed)  
* [ハーバード: Ginoを解雇 (2025年5月25日)](https://www.wgbh.org/news/education-news/2025-05-25/in-extremely-rare-move-harvard-revokes-tenure-and-cuts-ties-with-star-business-professor)
:::
::::

@@

* 日本の文系(<2000万円)だとFFPは割に合いません  
* 国立医薬品食品衛生研究所所長で1900万円くらい

結構ばれる: Ginoは追試、食品衛生部長は内部通報、Islamは経済学界の再現可能性指向

@@

貧乏くじ

@@

オッズをよく知らないまま、自ら進んで引くのは賢くない

@@

>>>>

---
title: |
  | 研究倫理
subtitle: |
  | 2025年6月19日(木)
  | 開発研究センター
  | ミクロ経済分析研究グループ
author: "伊藤成朗"
engine: knitr
format:
  revealjs: 
    standalone: true
    embed-resources: true
    slide-number: true
    width: 1600
    height: 900
    preview-links: auto
    logo: images/quarto.png
    footer: <http://seiroito.github.io/QuartoFiles/ethics/KenkyuRinri2025_slides.html>
    theme: sky
lightbox: auto
include-in-header:
  - text: |
      <style>
      #title-slide
       .title {
        font-size: 2.0em;
      }
      </style>
bibliography: ../seiro.bib
#### If it is 2 levels up, ../../seiro.bib
resources:
  - KenkyuRinri2025_slides.pdf
#### quarto render KenkyuRinri2025_slides.qmd
---
```{r read RefManageR library, echo=FALSE, warning = F}
library(RefManageR)
```
```{r setting, eval = T, cache = T, warning = F, message = F, echo = F}
library(RefManageR)
myBib <- ReadBib("c:/seiro/settings/TeX/seiro.bib")
BibOptions(max.names = 3)
```
```{r flair_color, eval = F, echo=FALSE}
library(flair)
red <- "#FF0000"
green <- "#00FF00"
blue <- "#0000FF"
```
```{css echo=FALSE}
.red {color: #FF0000;}
Green {color: #00FF00;}
.blue {color: #0000FF;}
White {
  color: white;
}
LightBlue {
  color: #33E7FF;
}
DarkBlue {
  color: #010638;
}
DBlue {
  color: dodgerblue;
}
Red {
  color: red;
}
Orange {
  color: #ff8442;
}
Yellow {
  color: yellow;
}
#### @font-face {
####   font-family: "hiragino";
####   #### src: url(../../../../../settings/fonts/HiraginoMinchoProW3.otf");
####   src: url("c:/seiro/settings/fonts/HiraginoMinchoProW3.otf");
#### }
@font-face {
  font-family: "Roboto";
  src: url("c:/seiro/settings/fonts/Roboto-Regular.ttf");
}
#### h1 {
####   font-size: 42pt;
####   font-family: 'hiragino';
####   color: black;
####   border-bottom: 1px;
####   border-color: rgb(248, 250, 252);
####   padding-bottom: 0pt;
#### }
p {
  #### font-size: 32pt;
  font-family: 'Roboto';
  color:white
}
.title{
  background-color=#010638;
}

@@

:::: {.fragment}
See a list of QRPs used in Dutch national survey (DNSRI) summarised [here](https://htmlpreview.github.io/?https://github.com/SeiroIto/PaperNotes/blob/main/QRPsInDutchNationalSurvey_Tufte.html)
::::

@@

:::: {.fragment}
::: {style="font-size:80%"}
* [Allegation](https://datacolada.org/109): Data tampering (FF) in several of her work on dishonesty (incl. with Dan Ariely!)  
* HBS: Put Gino on an unpaid admin leave, hired file forensic investigators, sent retraction requests to journals  
* Gino: Sued these folks and Harvard, asking for "at least $25 million" ([para 24, main document](https://www.courtlistener.com/docket/67659904/1/gino-v-president-and-fellows-of-harvard-college/))  
* [The problem, though, is that it will take years --- and be extraordinarily expensive --- to settle](https://www.vox.com/future-perfect/2023/8/9/23825966/francesca-gino-honesty-research-scientific-fraud-defamation-harvard-university#:~:text=The%20problem%2C%20though%2C%20is%20that%20it%20will%20take%20years%20%E2%80%94%20and%20be%20extraordinarily%20expensive%20%E2%80%94%20to%20settle)
* [150人あまりの共著者たちはどの論文は不正がないか調べる羽目に](https://www.science.org/content/article/after-honesty-researcher-s-retractions-colleagues-expand-scrutiny-her-work#:~:text=This%20week%2C%20Simonsohn%20and%20five%20other%20Gino%20co%2Dauthors%20emailed)  
* [ハーバード: Ginoを解雇 (2025年5月25日)](https://www.wgbh.org/news/education-news/2025-05-25/in-extremely-rare-move-harvard-revokes-tenure-and-cuts-ties-with-star-business-professor)
:::
::::

@@

:::: {.incremental}
* 日本の文系(<2000万円)だとFFPは割に合いません  
* 国立医薬品食品衛生研究所所長で1900万円くらい
::::

:::: {.fragment}
結構ばれる: Ginoは追試、食品衛生部長は内部通報、Islamは経済学界の再現可能性指向  
::::

@@

:::: {.fragment}
貧乏くじ
::::

@@

:::: {.fragment}
オッズをよく知らないまま、自ら進んで引くのは賢くない

@@

::::
